### 2020-08-14 paper/theory/model_executive_bargain.tex
incorporate changes in folder and add theory section

In this section, I use the canonical vote-buying model proposed by Groseclose and Snyder (1996) and Banks (2000) to model how mayors engage in patronage in Brazil. For any given term, a mayor wants to enact her preferred policy, which requires winning over potential resistance by the city council. The preferences of these legislators may vary: in some municipalities a mayor enjoys widespread political support ("base política"), while in others, the opposition ("oposição") garners more seats. In this battle over votes, patronage is the currency used to buy legislative votes.

I show that, in equilibrium, the cost of passing the mayor's preferred policy decreases monotonically as the legislative support for the mayor increases. Substantively, the model predicts that municipalities in which the mayor has more (less) councilors favorable to her, we should observe less (more) patronage. Below, I outline the setting of the model and derive key comparative statics that guide the empirical estimation of this paper.

@@

The mayor $M$ and opposition $O$ compete over legislative votes to enact their preferred policies. There are two possible outcomes: a policy $x$ favored by the mayor, and the status quo, denote as $y$, preferred by the opposition. In order to implement her policy the mayor must gain the approval of the city council, comprised of an odd $N$ number of voters, through a simple majority rule. The mayor and opposition spend political resources $W_M$ and $W_O$ to win over votes, which for the mayor includes patronage appointments into the public sector.

>>>>

In this section, I adapt the canonical vote-buying model proposed by Groseclose and Snyder (1996) and Banks (2000) to model how executive control over the city council determines patronage. The theoretical framework centers on two main actors, a government (\emph{governo}) and opposition (\emph{oposição}) who compete for votes in the city council.\footnote{I use the terms mayor and government interchangeably for the rest of this section.} The mayor seeks to enact her preferred policy, but can only do so by passing a simple majority vote in the council. The opposition, on the other hand, wants to block her efforts and maintain the status quo. In order to build a winning coalition, the mayor must spend a key political resource: patronage appointments into the municipal bureaucracy.

Ultimately, two forces shape the mayor's strategy: the amount of resources controlled by the opposition and the underlying preferences of the legislators. The key parameter of interest is the underlying preferences -- i.e. support for the mayor -- of city councilors. In some municipalities a mayor has widespread political support ("base política"), while in others, the opposition ("oposição") garners more seats. In the actual empirical estimation, we approximate these preferences by looking into the councilor's partisan alignments in the mayoral election. For the second determinant, the opposition's resource, it is clear that an opposition with more resources can better compete with the mayor, forcing the latter to spend more to deter them.

I show that, in equilibrium, the cost of passing the mayor's preferred policy decreases monotonically as the legislative support for the mayor increases. Substantively, the model predicts that municipalities in which the mayor has more (less) councilors favorable to her, we should observe less (more) patronage. In the remainder of this section, I outline the setting of the model and derive key comparative statics that guide the empirical estimation of this paper. I conclude with a discussion of the model and how it applies to the Brazilian municipal context.

@@

The government $G$ and opposition $O$ compete over legislative votes to enact their preferred policies. There are two possible outcomes: a policy $x$ favored by the government, and the status quo, denote as $y$, preferred by the opposition. In order to implement her policy the mayor must gain the approval of the city council, comprised of an odd $N$ number of voters, through a simple majority rule. The mayor and opposition spend political resources $W_M$ and $W_O$ to win over votes, which for the mayor includes patronage appointments into the public sector.

### 2020-08-14 paper/theory/notes_groseclose_et_snyder.tex
incorporate changes in folder and add theory section

\subsection*{Players:}
\begin{enumerate}
    \item Legislator: \textit{i}.
    \item Vote buyers: \{\textit{A}, \textit{B}\}
\end{enumerate}

@@

\subsection*{Preferences:}
For legislator $i$, denote the intensity of $i$'s preference of voting for $x$ over $s$ as

@@

For vote buyer \{\textit{A}, \textit{B}\}

>>>>

\subsection*{Players:}
\begin{enumerate}
    \item Legislator: \textit{i}.
    \item Vote buyers: $p \in \{A, B\}$
\end{enumerate}

@@

\subsection*{Preferences:}
For legislator $i$, denote the intensity of $i$'s preference of voting for $x$ over $s$ as:

@@

For vote buyer \{\textit{A}, \textit{B}\}, simply denote preferences over outcomes as:

$$W_{p \in \{A, B\}} = U_p(x) - U_p(s)$$

\subsection*{Strategies:}
Let $a(\cdot)$ and $b(\cdot)$ denote the bribe offer functions.
